Haul-out behavior and aerial survey detectability of seals in the Bering and Chukchi seas

### 2021-12-21 analysis/paper/London_HauloutBeahvior.Rmd
update docx template

---
title: "Haul-out behavior and aerial survey detectability of seals in the Bering and Chukchi seas"
author:
  - Josh M. London:
      email: josh.london@noaa.gov
      institute: [MML]
      correspondence: true
  - Paul B. Conn:
      institute: [MML]
      correspondence: false
  - Stacie K. Hardy:
      institute: [MML]
      correspondence: false
  - Erin L. Richmond:
      institute: [MML]
      correspondence: false
  - Jay M. Ver Hoef:
      institute: [MML]
      correspondence: false
  - Michael F. Cameron:
      institute: [MML]
      correspondence: false
  - Justin Crawford:
      institute: [ADFG]
      correspondence: false
  - Andrew L. Von Duyke:
      institute: [NSB]
      correspondence: false
  - Lori T. Quakenbush:
      institute: [ADFG]
      correspondence: false
  - Peter L. Boveng:
      institute: [MML]
      correspondence: false
institute:
  - MML: Marine Mammal Laboratory, Alaska Fisheries Science Center, NOAA Fisheries, Seattle, Washington, USA
  - ADFG: Arctic Marine Mammals Program, Alaska Department of Fish and Game, Fairbanks, Alaska, USA
  - NSB: Department of Wildlife Management, North Slope Borough, Utqiaġvik, Alaska, USA
output: 
  officedown::rdocx_document:
    reference_docx: ../templates/jml_template.docx
    pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks.lua
bibliography: references.json
link-citations: true
csl: ../templates/proceedings-of-the-royal-society-b.csl
always_allow_html: true
---

>>>>

---
title: "Haul-out behavior and aerial survey detectability of seals in the Bering and Chukchi seas"
author:
  - Josh M. London:
      email: josh.london@noaa.gov
      institute: [MML]
      correspondence: true
  - Paul B. Conn:
      institute: [MML]
      correspondence: false
  - Stacie K. Hardy:
      institute: [MML]
      correspondence: false
  - Erin L. Richmond:
      institute: [MML]
      correspondence: false
  - Jay M. Ver Hoef:
      institute: [MML]
      correspondence: false
  - Michael F. Cameron:
      institute: [MML]
      correspondence: false
  - Justin Crawford:
      institute: [ADFG]
      correspondence: false
  - Andrew L. Von Duyke:
      institute: [NSB]
      correspondence: false
  - Lori T. Quakenbush:
      institute: [ADFG]
      correspondence: false
  - Peter L. Boveng:
      institute: [MML]
      correspondence: false
institute:
  - MML: Marine Mammal Laboratory, Alaska Fisheries Science Center, NOAA Fisheries, Seattle, Washington, USA
  - ADFG: Arctic Marine Mammals Program, Alaska Department of Fish and Game, Fairbanks, Alaska, USA
  - NSB: Department of Wildlife Management, North Slope Borough, Utqiaġvik, Alaska, USA
output: 
  officedown::rdocx_document:
    reference_docx: ../templates/jml_template.docx
    pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks.lua
    page_size:
      width: 8.5
      height: 11
      orient: "portrait"
    page_margins:
      bottom: 1.25
      top: 1.25
      right: 1.0
      left: 0.5
      header: 0.5
      footer: 0.5
      gutter: 0.5
bibliography: references.json
link-citations: true
csl: ../templates/proceedings-of-the-royal-society-b.csl
always_allow_html: true
---
